Prestige bias in cultural evolutionary dynamics

### 2024-05-07 ms/ms.tex
typo

Henrich and Gil-White~\citep{prestige_evolution} noted that ``the most skilled/knowledgeable role-models will, on average, end up with the biggest and most lavish clienteles, so the size and lavishness of a given model's clientele size (the \emph{prestige}) provides a convenient and reliable proxy for that person's information quality''.
Thus, they predicted that skilled individuals have higher status, that people preferentially copy high-status individuals, and therefore that prestigious individuals may be influential even beyond their domain of expertise. 
They defined prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature \citep{prestige_evolution} .
Similarly, the New Oxford American Dictionary defines prestige as the ``widespread respect and admiration felt for someone or something on the basis of a \emph{perception} of their achievements or quality.''.
Chudek et al.~\citep{prestige_cultural_learning} have also defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'' and demonstrated its occurrence in 3-4 year old children.
Nakata et al.~\citep{Nakata2024} define such a bias as a ``prestige bias based on second-order cues,'' in which ``Social learners can use the extent of attention and the amount copied from others as cues for prestige.''
Henrich and Broesch~\citep{fijian_social_bias} have further suggested that prestige bias can, over generations, lead to cultural adaptations and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.

>>>>

Henrich and Gil-White~\citep{prestige_evolution} noted that ``the most skilled/knowledgeable role-models will, on average, end up with the biggest and most lavish clienteles, so the size and lavishness of a given model's clientele size (the \emph{prestige}) provides a convenient and reliable proxy for that person's information quality''.
Thus, they predicted that skilled individuals have higher status, that people preferentially copy high-status individuals, and therefore that prestigious individuals may be influential even beyond their domain of expertise. 
They defined prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature \citep{prestige_evolution} .
Similarly, the New Oxford American Dictionary defines prestige as the ``widespread respect and admiration felt for someone or something on the basis of a \emph{perception} of their achievements or quality.''
Chudek et al.~\citep{prestige_cultural_learning} have also defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'' and demonstrated its occurrence in 3-4 year old children.
Nakata et al.~\citep{Nakata2024} define such a bias as a ``prestige bias based on second-order cues,'' in which ``Social learners can use the extent of attention and the amount copied from others as cues for prestige.''
Henrich and Broesch~\citep{fijian_social_bias} have further suggested that prestige bias can, over generations, lead to cultural adaptations and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
